---
title: "pHackCOVID19"
author: "hank"
date: "2020-09-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r read data}

library(utils)
library(broom)
library(tidyverse)

# Read in the data
covid19Data <- read.csv('https://opendata.ecdc.europa.eu/covid19/casedistribution/csv', 
                        na.strings = "", fileEncoding = 'UTF-8-BOM')

```

```{r pval loop}

# Lets loop over days, regressing each day's country/territory case count on the square of the number of letters in each country's name :D

# Empty vector for pvals
pvals <- c()

for (day in 1:length(unique(covid19Data$dateRep))){

  # Get the data for this day
  thisDaysData <- covid19Data[(covid19Data$dateRep == as.character(covid19Data$dateRep[day])), ]
  
  # Get the length of the country/territory names and square it
  thisDaysData$nameLenSquared <- nchar(thisDaysData$countriesAndTerritories)^2

  # Build the model
  model <- lm(cases ~ nameLenSquared, 
              data=thisDaysData)
  
  # Glance at it and grab the p-value
  g <- glance(model)
  pval <- as.double(g[, "p.value"])
  pvals <- c(pvals, pval)

}

```

```{r pval hists}

# Lets look at the distributions of the p-values across the days
hist(pvals)

# What is the proportion of pvals that are significant at alpha = 0.05?
length(pvals[pvals < 0.05])  / length(pvals[pvals > 0.05]) 

```

The histogram of p-values looks closer to a uniform distribution than a normal, so this suggests (as we know) that there is no significant relationship between these variables when "bootstrapping" this model across days.

However, the number of p-values that are deemed significant is not a trivial amount...
If one were to perform this analysis on a random day, there is a 17% chance that they would find a p-value deemed significant by alpha = 0.05. This illustrates that if an analysis like this is data-starved, ie only performed on a single day, there is a decent likelihood that a false conclusion could be reached. To correct for this, it is useful to test the potential observation of significant p-value by performing the same analysis on other days. To take it a step further, one should train the model on a subset of the days and test it on the remaining held-out set of days. We suggest that if this was performed there would be no significant result discovered. 

# Tried cross validation but the result was not obviously interpretable...

# ```{r cval}
# 
# library(lmvar)
# 
# # Get the length of the country/territory names and square it for the whole dataset
# covid19Data$nameLenSquared <- nchar(covid19Data$countriesAndTerritories)^2
# 
# # Define the model
# model = lm(cases ~ nameLenSquared, covid19Data, x = TRUE, y = TRUE)
# 
# # Cross validate it across days
# cv = cv.lm(model, log = TRUE, ks_test = TRUE)
# 
# ```


